\documentclass[12pt]{article}

\addtolength{\textwidth}{1in}
\addtolength{\oddsidemargin}{-.5in} %left margin
\addtolength{\evensidemargin}{-.5in}
\setlength{\textheight}{8.5in}
\setlength{\topmargin}{-.5in}
\setlength{\headheight}{18.0pt}
\setlength{\footskip}{.375in}
\renewcommand{\baselinestretch}{1.0}
\linespread{1.2}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{1pt}
\lhead{Trade Agreements in the Shadow of Lobbying}
%\chead{}
\rhead{Kristy Buzard}
%\fancyfoot[C]{}
%\fancyhead[R]{}

\usepackage[pdftex,
bookmarks=true,
bookmarksnumbered=false,
pdfview=fitH,
bookmarksopen=true]{hyperref}
\usepackage[pdftex]{graphicx}
\setcounter{secnumdepth}{-1}


\usepackage[usenames,dvipsnames]{color}
\usepackage{cite}
\usepackage{times, verbatim,bm,pifont}
\usepackage{amsbsy,amssymb, amsmath, amsthm, MnSymbol,bbding}


\begin{document}

\begin{center}
\large Response to Editor and Referee \\
\normalsize February 2, 2016
\end{center}

Editor's point $\#$2: I have created four subsections within Section 2 to structure the exposition of the model. I think this is much clearer than the previous draft.

Editor's point $\#$3: Thank you for the suggestion to add an extensive form and to define the game more clearly and formally. I think the addition of the normal form in Figure 1 made this portion of the paper significantly more readable. I hope you will agree. The discussion of the players, timing, and the presentation of the extensive form are at the end of Section 2.1 (The Basic Setup). I largely allow the extensive form to do the work of laying out the strategy spaces so as not to clutter the text. The payoffs are gathered together in their own section (2.2: Preferences).

Editor's point $\#$4: I have added a traded numeraire good to address the concern about balanced trade. As all the results hinge on the incentives of the lobby, the executive and the median legislator---none of which are impacted by the addition of the numeraire good---this does not change any of the results. In carefully examining this issue, I realized that it would be more complete to include labor income in the welfare functions of the executive and lobby (again, this would change no results, as they all involve either differencing two welfare terms or taking derivatives with respect to a tariff). However, since much of the literature I'm following abstracts from a balanced trade condition and a numeraire sector with labor input, this would complicate the exposition and comparison to the extant literature. I have therefore chosen to insert Footnote [{\color{blue}ADD FOOTNOTE REFERENCE}] to this effect. It would be a simple matter to put labor income into the welfare functions if that is judged preferable.

Editor's point $\#$5: I have added expectations operators to Equations (3) and (4) [{\color{blue}CHECK EQ:JV AND EQ:LV}] to address the redundant notation. Thank you for pointing out this needed clarification.

Editor's point $\#$6: I have rewritten the passage about the influence of lobbying on the executive to read
\begin{quote}
  This setup does not strictly require that the executives are not lobbied. The assumption that the weight the executives place on import-competing profits is constant only requires that the extent to which they favor this industry cannot be \textit{directly} influenced by lobbying effort. The assumption is innocuous as long as the executives' preferences are not directly altered in a significant way by lobbying over trade.
\end{quote}
I think this is a softer claim than what was in the earlier draft and avoids getting into an interpretation of exactly what `Protection for Sale' means in this context since this is not central---what is important is to defend the modeling assumption directly.

I have also removed the duplicate statement of Assumption 1 and combined redundant text surrounding the two statements. I have added $\forall e$ to the statement of Assumption 1.

Editor's point $\#$7: Thank you for pointing out that the second order condition holds everywhere and that the proof of what was formerly Lemma 1 can be drastically simplified. I moved the discussion of the second order condition into the text and integrated it with the simple result on the increasingness of trade war tariff in the political economy weight. As this did not need to be referenced elsewhere and no longer requires a proof in the appendix, it is no longer labeled Lemma 1. Likewise, Lemma 0 is no longer necessary and has been removed. Note that this advances the numbering of the lemmas in the revised draft relative to the previous draft. 

Editor's point $\#9$: I have added the move of nature that determines whether the legislature gets the opportunity to the extensive form and to the discussion of the timing in the initial discussion of the model (Section 2.1: The Basic Setup). I have gathered all relevant discussion in this section as suggested.

Editor's point $\#10$: I have removed the extensions (Section 6) per your suggestion. {\color{blue}ADD discussion about fixing exposition around one break at a time}

Referee's point $\#1$ (``Introduction is derailing at the start''):

Referee's point $\#2$ (``Intuition in the Introduction about political uncertainty''):

Referee's point $\#3$ (``Parliamentary democracies''): I have added a paragraph at the very end of Section 2 to address this concern. I would also note, as a point of interest, that the number of veto points does not always correlate particularly well with the political system. I was not easily able to find empirical work on the number of veto points on trade issues for Turkey, but Sparkes, Bump and Reich (2015) were somewhat surprisingly able to identify \textit{seven} veto points for health issues in Turkey.\footnote{Sparkes, S.P., Bump, J. B. and M. R. Reich (2015), ``Political Strategies for Health Reform in Turkey: Extending Veto Point Theory,'' \textit{Health Systems and Reform}, 1(4), 263-275.}

Referee's point $\#4$ (``Strong language regarding contribution''):



\end{document}